---
title: "Globally robust confidence intervals"
author: "Matias Salibian"
date: "July 25, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Globally robust confidence intervals for simple linear regression models

This repository contains `R` code implementing 
the 
globally robust confidence intervals for the slope of a simple linear regression model 
as proposed in 
[Adrover, J. and Salibian-Barrera, M. (2010)](http://dx.doi.org/10.1016/j.csda.2009.05.005).

The functions are in the file `rci-pub.R`. The following example
illustrates how to 
use this code. First, load the functions and generate a simple 
data set
```{r first}
source('rci-pub.R')
set.seed(123)
n <- 30
x <- rexp(n, rate=.5)
y <- 2 - x + rnorm(n, sd=.7)
```
A scatter plot of the data and both robust
and least squares fits can be obtained with
```{r scatter}
plot(y ~ x, pch=19, col='gray', cex=1.5, ylim=c(-6, 6))
library(robustbase)
fit.rob <- lmrob(y~x)
fit.ls <- lm(y~x)
abline(fit.rob, lwd=6, col='steelblue')
abline(fit.ls, lwd=2, col='red')
```

The estimated coefficients are
```{r coefs}
coef(fit.rob)
coef(fit.ls)
```
The globally robust 95% confidence
interval for the slope, protected against 
up to 5% of outliers in the data is
```{r cino}
slope.ci(x=x, y=y, alpha=.05, epsilon=.05)
```

We now add outliers to the data. 
```{r outs}
ou <- rbinom(n, size=1, prob=.05)
y[ou==1] <- rnorm(sum(ou), mean=5, sd=.1)
x[ou==1] <- rnorm(sum(ou), mean=7, sd=.1)
```
The data and the LS and robust fits now look like this:
```{r scatterout}
plot(y ~ x, pch=19, col='gray', cex=1.5, ylim=c(-6, 6))
points(y[ou==1] ~ x[ou==1], pch=19, col='gray30', cex=1.5)
fit.rob <- lmrob(y~x)
fit.ls <- lm(y~x)
abline(fit.rob, lwd=6, col='lightblue')
abline(fit.ls, lwd=2, col='orange')
```

The estimated coefficients are
```{r coefsout}
coef(fit.rob)
coef(fit.ls)
```
The globally robust 95% confidence
interval for the slope, protected against 
up to 5% of outliers in the data is
```{r grciout}
slope.ci(x=x, y=y, alpha=.05, epsilon=.05)
```

